\documentclass[11pt,a4paper,sans]{moderncv}

% ModernCV themes
\moderncvstyle{banking} % Style options: casual, classic, banking, etc.
\moderncvcolor{blue}    % Color options: blue, orange, green, red, etc.

% Adjust page margins
\usepackage[scale=0.75]{geometry}

% Font fixes
\usepackage{lmodern} % Use scalable Latin Modern fonts
\usepackage[T1]{fontenc} % Ensure proper font encoding

% Personal data
\name{Aohan}{He}
\title{Senior Software Engineer | Machine Learning and Vision Specialist} % Updated title
\address{Queenstown}{Singapore, 140051} % Optional
\phone[mobile]{+65 84635846} % Optional
\email{heaohan@gmail.com} % Optional
\social[linkedin]{heaohan} % Optional
\social[github]{heaohan} % Optional

%----------------------------------------------------------------------------------------
%	CONTENT
%----------------------------------------------------------------------------------------

\begin{document}

% Name and title
\makecvtitle

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}
\cventry{2016--2020}{PhD in Mechanical Engineering}{National University of Singapore}{}{}{
    \begin{itemize}
        \item Focused on phase retrieval techniques for optical applications, including surface, displacement, and strain measurement.
        \item Developed CUDA-based GPU acceleration for optical coherent methods.
        \item Gained expertise in image processing, optics, and programming (C++, MATLAB, CUDA).
    \end{itemize}}
\cventry{2011--2015}{Bachelor in Measurement Control and Information Technology}{Beihang University}{}{}{
    \begin{itemize}
        \item Specialized in optics, computer science, control systems, and signal processing.
        \item Conducted research on rail wheel diameter measurement and laser structure light.
        \item Graduated with top academic distinction based on GPA.
    \end{itemize}}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Experience}
\cventry{2022--Present}{Senior Engineer}{Seagate Singapore International Headquarters Pte. Ltd.}{}{}{
\begin{itemize}
    \item Designed and implemented machine vision algorithms for high-precision assembly equipment, including pick-and-place tasks and defect detection.
    \item Developed a hybrid rule-based and machine learning vision system for transferring slider bars.
    \item Integrated CI/CD pipelines using GitHub Actions for automated software development.
    \item Collaborated with cross-functional teams to design scalable software architectures for automated inspection systems.
\end{itemize}}

\cventry{2020--2022}{Software Engineer}{Semiconductor Technologies \& Instruments Pte Ltd}{}{}{
\begin{itemize}
    \item Designed advanced image processing algorithms for wafer inspection, including edge defect detection and bump height measurement.
    \item Spearheaded the development of deep learning-based segmentation models.
    \item Developed and optimized 3D inspection modules with laser profiling and confocal microscopy, including 3D UI displays and rigorous reliability testing.
    \item Optimized software pipelines for high-throughput inspection systems.
\end{itemize}}

\cventry{2016--2020}{PhD Candidate}{National University of Singapore}{}{}{
\begin{itemize}
    \item Conducted research on phase retrieval techniques for optical metrology, publishing three peer-reviewed papers.
    \item Developed GPU-accelerated algorithms for optical coherent methods, achieving significant computational efficiency.
    \item Designed and implemented experimental setups for surface and strain measurement using advanced imaging techniques.
\end{itemize}}

\cventry{2016--2019}{Teaching Assistant}{National University of Singapore}{}{}{
\begin{itemize}
    \item Assisted in teaching modules such as Mechanics of Machines, Engineering Principles and Practice, and Mechanics of Materials.
    \item Mentored undergraduate students in research projects involving image processing and system design.
\end{itemize}}

%----------------------------------------------------------------------------------------
%	HONORS AND AWARDS
%----------------------------------------------------------------------------------------

\section{Honors and Awards}
\cvitem{2016--2020}{\textbf{Research Scholarship}, National University of Singapore}
\cvitem{2013}{\textbf{National Scholarship of China} (Top 0.2\% of students nationwide)}
\cvitem{2012--2014}{\textbf{First-Prize Scholarship}, Beihang University}
\cvitem{2013}{\textbf{Honorable Mention}, Mathematical Contest in Modeling}

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS
%----------------------------------------------------------------------------------------

\section{Technical Skills}
\cvitemwithcomment{Programming Languages}{C++, Python, MATLAB, CUDA, C\#}{Proficient}
\cvitemwithcomment{Machine Learning}{TensorFlow, PyTorch, Cognex VisionPro, Halcon}{Experienced}
\cvitemwithcomment{Computer Vision}{OpenCV, Scikit-Image, Halcon, Cognex}{Experienced}
\cvitemwithcomment{Machine Vision}{Optics, Camera Calibration, Vision-Guided Robot Control}{Experienced}
\cvitemwithcomment{Software Development}{Agile Development, Git, CI/CD (GitHub Actions)}{Proficient}
\cvitemwithcomment{System Design}{Distributed Systems, Data-Intensive Applications}{Intermediate}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------

\section{Projects}
\cvitem{2025}{\textbf{Vision System for Slider Bar Transfer Equipment}}
\begin{itemize}
    \item Designed a machine vision system for real-time measurement and guidance for Slider Bar Transfer Equipment.
    \item Implemented an algorithm to locate the slider bars that are not covered by any other bar.
    \item Implemented measurement and guidance vision function using rule-based method.
    \item Implemented DL classification model for tray type classification.
    \item Implemented vision sequence for hardware triggered camera.
    \item Designed auto teach and calibration sequence.
\end{itemize}

\cvitem{2025}{\textbf{Vision System for Hard Drive Assembly Equipment}}
\begin{itemize}
    \item Designed a machine vision system for real-time measurement and guidance for Hard Drive Assembly Equipment.
    \item Implemented a capture and processing sequence for a high-speed camera by closely cooperating with the robot control system.
    \item Designed auto teach and calibration sequence.
    \item Implemented measurement and guidance vision function using rule-based method.
    \item Implemented CI/CD pipelines for seamless deployment of station software.
\end{itemize}

\cvitem{2025}{\textbf{CI/CD for Department Software Repositories}}
\begin{itemize}
    \item Implemented CI/CD pipelines for seamless deployment of station software.
    \item Added features and fix bugs for common libraries Repositories.
    \item Implemented CI/CD pipelines for common libraries Repositories.
    \item Persuaded the team to adopt CI/CD practices, resulting in improved software quality and faster deployment cycles.
\end{itemize}

\cvitem{2024}{\textbf{Disk and Spacer Assembly Simulation}}
\begin{itemize}
    \item Simulated assembly process with disks and spacers from different vendors to estimate the assembly quality with different parts control strategies.
    \item Implemented the simulation using Python and wrote the unit test using PyTest.
\end{itemize}

\cvitem{2023}{\textbf{Vision System for Auto Screw Install Station}}
\begin{itemize}
    \item Designed a machine vision system for real-time measurement and guidance for Auto Screw Install Station.
    \item Located a slowdown issue caused by the control software vendor by carefully designing a test sequence and using Git.
    \item Designed auto teach and calibration sequence.
    \item Implemented measurement and guidance vision function using rule-based method.
    \item Implemented CI/CD pipelines for seamless deployment of station software.
\end{itemize}

\cvitem{2023}{\textbf{Vision System for Auto Glue Dispenser Station}}
\begin{itemize}
    \item Conducted a proof-of-concept study for the machine vision system using Halcon for the Auto Glue Dispenser Station.
    \item Integrated rule-based method for localization and ML method for anomaly detection.
    \item Use rule-based method to measure glue droplet to trigger the robot axis movement.
\end{itemize}

\cvitem{2022}{\textbf{Deep Learning Inspection Module for Wafer Inspection Vision System}}
\begin{itemize}
    \item Developed software part for Deep Learning Module.
    \item Integrated Cognex Vidi to the module.
    \item Conducted extensive testing and deployment support to ensure robustness and reliability in production environments.
\end{itemize}

\cvitem{2022}{\textbf{Wafer Edge Inspection Module for Wafer Inspection Vision System}}
\begin{itemize}
    \item Developed software part for Wafer Edge Inspection Module.
    \item Cooperated with Control Software Engineer to define the inspection and calibration sequence.
    \item Conducted extensive testing and deployment support to ensure robustness and reliability in production environments.
\end{itemize}

\cvitem{2021}{\textbf{3D Inspection Module for Wafer Inspection Vision System}}
\begin{itemize}
    \item Developed software part for 3D Inspection Module.
    \item Optimized existing laser profiling system for 3D Inspection Module.
    \item Integrated Confocal Microscopy System for 3D Inspection Module.
    \item Developed 3D UI Display for 3D Inspection Module.
    \item Conducted extensive testing to ensure robustness and reliability in production environments.
\end{itemize}

\cvitem{2020}{\textbf{Recipe Load Optimization for Wafer Inspection Vision Software}}
\begin{itemize}
    \item Optimized recipe load process: located the bottleneck, i.e., FOV and Dice map generation, and optimized it.
\end{itemize}

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS
%----------------------------------------------------------------------------------------

\section{Certifications}
\cvitem{2023}{\textbf{MVTEC Halcon Certification}, Advanced Machine Vision Development}
\cvitem{2022}{\textbf{LinkedIn Learning}, Advance Your Skills in AI and Machine Learning}
\cvitem{2022}{\textbf{PMI-ACP Certification Preparation}, Agile Methodologies}

% Add Continuous Learning Section
\section{Continuous Learning}
\cvitem{Machine Learning}{
    \begin{itemize}
        \item Completed courses on advanced NLP, GANs, and deep learning optimization.
        \item Certifications in AI and machine learning from platforms like TensorFlow and PyTorch.
    \end{itemize}}
\cvitem{Software Engineering}{
    \begin{itemize}
        \item Read books like \textit{Head First Design Patterns}, \textit{The Pragmatic Programmer}, and \textit{Head First Software Development}.
        \item Completed courses on object-oriented design, software architecture, and design patterns.
        \item Gained expertise in SOLID principles, refactoring, and clean code practices.
    \end{itemize}}
\cvitem{System Design}{
    \begin{itemize}
        \item Studied books like \textit{Designing Data-Intensive Applications} and \textit{System Design Interview}.
    \end{itemize}}

%----------------------------------------------------------------------------------------
%	RESEARCH EXPERTISE
%----------------------------------------------------------------------------------------

\section{Research Expertise}
\cvitem{Phase Retrieval Techniques}{
    \begin{itemize}
        \item Developed swarm intelligence algorithms (APSO, DE) for phase retrieval in optical metrology.
        \item Implemented CUDA acceleration for two-shot techniques, achieving better computational efficiency.
        \item Designed simplified paraboloid phase models and Hilbert spiral transforms for fringe direction estimation.
    \end{itemize}}
\cvitem{Publications}{Published journal articles on optical cryptosystems, phase tracking, and fringe pattern analysis, contributing to both theoretical advancements and practical validations.}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------

\section{Publications}
\cvitem{2019}{\textbf{A. He} and C. Quan, "Wavefront correction for spatial nonuniformity of the liquid crystal on silicon based spatial light modulator," \textit{Optics and Lasers in Engineering}, vol. 121, pp. 377–388.}
\cvitem{2018}{\textbf{A. He} and C. Quan, "An improved principal component analysis based region matching method for fringe direction estimation," \textit{Optics Communications}, vol. 413, pp. 87–102.}
\cvitem{2017}{\textbf{A. He}, B. Deepan, and C. Quan, "Simplified paraboloid phase model-based phase tracker for demodulation of a single complex fringe," \textit{Applied Optics}, vol. 56, pp. 7217–7224.}

\end{document}
